Normalization Example using spike-in control as a standard

### 2017-08-07 examples/Example_003_ER_H2av.Rmd
Created simiplified examples of the analyses in the ./examples subdirectory.

---
title: "Normalization Example using internal CTCF peaks as a standard"
author: "Andrew Holding"
date: "8/7/2017"
output: pdf_document
---

@@

```{r brundle}
source('../package/brundle.R')
```

@@

```{r}
jg.controlMinOverlap      <- 5
jg.controlSampleSheet     <- "samplesheet/samplesheet_SLX14438_hs_CTCF_DBA.csv"
jg.experimentSampleSheet  <- "samplesheet/samplesheet_SLX14438_hs_ER_DBA.csv"
jg.treatedCondition       =  "Fulvestrant"
jg.untreatedCondition     =  "none"

@@

```{r}
filename<-"Rdata/example_001_SLX-14438_dba_human_ER_CTCF.rda"
if(!file.exists(filename)){
  dbaExperiment <- jg.getDba(jg.experimentSampleSheet, bRemoveDuplicates=TRUE)
  dbaControl    <- jg.getDba(jg.controlSampleSheet, bRemoveDuplicates=TRUE)
  save(dbaExperiment,dbaControl,file=filename)
} else {
  load(filename)
}

@@

```{r}
jg.dba_analysis<-dba.analyze(jg.dba)
dba.plotMA(jg.dba_analysis,bFlip=TRUE)

@@

```{r}
write.csv(dba.report(jg.dba_analysis),file="results/Example_001.csv")
```

>>>>

---
title: "Normalization Example using spike-in control as a standard"
author: "Andrew Holding"
date: "8/7/2017"
output: pdf_document
---

@@

```{r brundle, results='hide', message=FALSE, warning=FALSE}
source('../package/brundle.R')
```

@@

```{r}
dbaSummits                <- 200
jg.controlMinOverlap      <- 5
jg.controlSampleSheet     <- "samplesheet/samplesheet_SLX8047_dm.csv"
jg.experimentSampleSheet  <- "samplesheet/samplesheet_SLX8047_hs.csv"
jg.treatedCondition       =  "Fulvestrant"
jg.untreatedCondition     =  "none"

@@

```{r}
filename<-"Rdata/example_003_SLX-8047_dba_HsDm.rda"
if(!file.exists(filename)){
  dbaExperiment <- jg.getDba(jg.experimentSampleSheet, bRemoveDuplicates=TRUE)
  dbaControl    <- jg.getDba(jg.controlSampleSheet, bRemoveDuplicates=TRUE)
  save(dbaExperiment,dbaControl,file=filename)
} else {
  load(filename)
}

@@

```{r}
jg.dba_analysis<-dba.analyze(jg.dba)
dba.plotMA(jg.dba_analysis)

@@

```{r}
write.csv(dba.report(jg.dba_analysis),file="results/Example_003.csv")
```
